Draft Article

### 2019-08-16 article.tex
added bib

% \addbibresource{article.bib}

@@

Internal investigators determined that OPM had been compromised by an advanced persistent threat (APT), a formally organized and typically state-sponsored group of hackers. US officials would only confirm that they believed a \enquote{foreign entity or government} had been behind the attack, but it was an open secret at the time that they suspected the involvement of the Chinese government.\footcite{spetalnick_china_2015} The APT made identification easy by leaving their calling-card: the trojan opmsecurity.org domain was registered in the name of \enquote{Steve Rogers,} the Marvel comics character better known as Captain America. This virtual taunt, along with Chinese-based email and IP addresses, all but guaranteed that the attack had come from an APT sponsored by the Chinese government, likely the Chinese military's cyber-espionage division.

@@

>>>>

\addbibresource{article.bib}

@@

@@

Internal investigators determined that OPM had been compromised by an advanced persistent threat (APT), a formally organized and typically state-sponsored group of hackers. US officials would only confirm that they believed a \enquote{foreign entity or government} had been behind the attack, but it was an open secret at the time that they suspected the involvement of the Chinese government.\footcite{spetalnick_china_2015} The APT made identification easy by leaving their calling-card: the trojan opmsecurity.org domain was registered in the name of \enquote{Steve Rogers,} the Marvel comics character better known as Captain America. This virtual taunt, along with the Chinese-based email and IP addresses, all but guaranteed that the attack had come from an APT sponsored by the Chinese government, likely the Chinese military's cyber-espionage division.\footcite{koerner_inside_2016} Nonetheless, the US government refused to name China as the culprit.
